Holomorphic field theories and higher algebra

### 2024-09-19 draft.tex

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!

\owen{Laying out some of this stuff in an attempt to state Minghao's theorem}

We will allow graphs with finitely many vertices and edges, 
but also leaves (also known as hair or half-edges).\footnote{That is, a vertex may have, in addition to edges connecting it to other vertices, some incident edges that do not connect to another vertex. 
These will label inputs to an operation associated to the graph.}
We allow multiple edges between vertices, as well as loops.

For a graph $\gamma$, let $E(\gamma)$ denote the number of edges,
$V(\gamma)$ denote the number of vertices,
and $L(gamma)$ denote the number of leaves.

\begin{dfn}
For a graph $\gamma$, there is a space $\RR_+^{E(\gamma)}$ parametrizing the moduli space of lengths (all positive) given to the edges.
This positive orthant has a the partial compactification $\Schw(\gamma)$, known as the {\em Schwinger space} of $\gamma$, 
where \owen{define!} 
\end{dfn}

\begin{dfn}
For a perturbative holomorphic field on $\CC^d$ with space of fields 
\[
\cV = \Gamma(\CC^d, \Omega^{0,\bullet}(V)),
\] 
as defined in Section~\ref{}, 
there is a family of distributions
\[
w_{\gamma, t}: \cV_c^{L(\gamma)} \to \CC
\]
parametrized by $t \in \RR_+^{E(\gamma)}$,
known as the {\em regularized weight of $\gamma$}.
\end{dfn}

This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
where each edge $e$ is labeled by a smooth function $P_{t(e)}$ depending on the length of the edge and where each vertex is labeled by a distribution arising from an interaction term of the theory.
For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
The putative integrals become divergent.

For holomorphic field theories, however, something remarkable happens.

\begin{thm}[Wang, \owen{precise citations}]
For every graph~$\gamma$,
this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
That is, there is a smooth map
\[
w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
\]
where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.it 
\end{thm}

>>>>

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory was developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.

Recently, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!
We briefly recall the approach to this regulation scheme.

We will allow graphs with finitely many vertices and edges, 
but also leaves (also known as hair or half-edges).\footnote{That is, a vertex may have, in addition to edges connecting it to other vertices, some incident edges that do not connect to another vertex. 
These will label inputs to an operation associated to the graph.}
We allow multiple edges between vertices, as well as loops, the precise form of which are determined by the interactions of the theory.

For a graph $\gamma$, let $E(\gamma)$ denote the number of edges,
$V(\gamma)$ denote the number of vertices,
and $L(\gamma)$ denote the number of leaves.
The scheme begins with the familiar Wilsonian approach to renormalization which involves introducing an IR `cut-off' length scale $L > 0$.
The \textit{Schwinger space} associated to a graph $\gamma$ and a length $L$ is the non-compact manifold with corners $(0,L]^{E(\gamma)}$, which we will denote $\op{Schw}(\gamma)$ below.
The desired Feynman graph weight $W_\gamma$ of a graph $\gamma$ is obtained as the integral over  Scwhinger space.

\begin{dfn}
For a perturbative field theory with space of fields $\cE$, there is a distribution valued in forms on Schwinger space
\[
w_{\gamma} \colon \cE^{L(\gamma)}_c \to \Omega^\bu \left( \op{Schw}(\gamma) \right)
\]
which we call the {\em regularized weight of $\gamma$}.
\end{dfn}

The possibly ill-defined weight $W_\gamma$ is obtained by integration of $w_\gamma$ over Schwinger space.
This family of distributions is constructed as an integral over $\CC^{v(\gamma) d}$,
where each edge $e$ is labeled by a smooth function $P_{t(e)}$ depending on the length of the edge and where each vertex is labeled by a distribution arising from an interaction term of the theory.
For general theories, one cannot smoothly continue the regularized weight from the positive length values to zero lengths.
The putative integrals become divergent, which is reflected by the non-compactness of Schwinger space from this perspective.

For holomorphic field theories (and generally topological-holomorphic theories, see \cite{WWthf}) however, something remarkable happens.

\begin{thm}[Wang, \owen{precise citations}]
Let $\cE$ be the space of fields underlying a holomorphic field theory on $\C^n$.
For every graph~$\gamma$, $w_{\gamma}$ has a natural smooth extension $\til {w_\gamma}$ to a compactification $\til{\op{Schw}(\gamma)}$ of Schwinger space.
In particular, the weight
\[
W_\gamma \colon \cE^{L(\gamma)}_c \xto{\til{w_\gamma}}\Omega^\bu \left( \til{\op{Schw}(\gamma)} \right) \xto{\int} \C
\]
is a continuous linear functional on $\cE_c^{L(\gamma)}$.
\end{thm}
